Dark Control: The Default Mode Network as a Reinforcement Learning Agent

### 2018-08-11 paper/paper.tex

\subsubsection{Accumulated rewards and policies}
The behavior of the agent is governed by a \textit{policy}, which maps states of the world
to probability distributions over candidate actions.
Starting at time $t=0$,
following a policy $\pi$ generates a trajectory of action choices:
\begin{eqnarray*}
  \begin{split}
    \textbf{choose action: }a_0 &\sim \pi(a|s_0)\\
    \textbf{ observe transition: }s_1 &\sim p(s|s_0,a_0)\textbf{ and collect
      reward }R_0 = r(s_0, a_0, s_1)\\
    \textbf{choose action: }a_1 &\sim \pi(a|s_1)\\
    \textbf{ observe transition: }s_2 &\sim p(s|s_1,a_1), \textbf{ and collect
      reward }R_1 = r(s_1, a_1,s_2)\\
    \vdots\\
    \textbf{choose action: }a_{t} &\sim \pi(a|s_{t})\\
    \textbf{ observe transition: }s_{t+1} &\sim p(s|s_{t},a_{t}), \textbf{ and
      collect reward }R_{t} = r(s_{t}, a_{t},s_{t+1})\\
    \vdots
  \end{split}
\end{eqnarray*}
We assume time invariance
in that we expect the dynamics of the process
to be equivalent over sufficiently long time windows of equal length (i.e., stationarity).
Since an action executed in the present moment might have repercussions in the
far future, it turns out that the quantity to optimize is not the instantaneous
rewards $r(s, a)$, but a \textit{cumulative reward} estimate which takes into
account expected reward from action choices in the future. A common approach to
modeling this gathered outcome is the time-discounted cumulative reward% function
\begin{equation}
  \label{eq:cumr}
  G^\pi = \sum_{t=0}^{\infty}\gamma^{t}R_t = R_0 + \gamma R_1 + \gamma^2 R_2 + \ldots + \gamma^tR_t + \ldots
\end{equation}
This random variable
  \footnote{The reward outcome is random as it depends both on the environment's dynamics and the
  policy $\pi$ being executed. The exponential delay discounting function used
  here refers to the usual formulation in the field of reinforcement learning,
  although psychological experiments may also reveal other discounting regimes
  \citep{green2004discounting}.}
measures the cumulative reward of
following an action policy $\pi$.
%
Note that value buffering may be realized in the vmPFC by virtue of
this region's connections to the NAc of the reward sytem
\citep{carlezon2009}.

>>>>

\subsubsection{Accumulated rewards and policies}
The behavior of the agent is governed by a \textit{policy}, which maps states of the world
to probability distributions over candidate actions.
Starting at time $t=0$,
following a policy $\pi$ generates a trajectory of action choices:
\begin{eqnarray*}
  \begin{split}
    \textbf{choose action: }a_0 &\sim \pi(a|s_0)\\
    \textbf{ observe transition: }s_1 &\sim p(s|s_0,a_0)\textbf{ and collect
      reward }R_0 = r(s_0, a_0, s_1)\\
    \textbf{choose action: }a_1 &\sim \pi(a|s_1)\\
    \textbf{ observe transition: }s_2 &\sim p(s|s_1,a_1), \textbf{ and collect
      reward }R_1 = r(s_1, a_1,s_2)\\
    \vdots\\
    \textbf{choose action: }a_{t} &\sim \pi(a|s_{t})\\
    \textbf{ observe transition: }s_{t+1} &\sim p(s|s_{t},a_{t}), \textbf{ and
      collect reward }R_{t} = r(s_{t}, a_{t},s_{t+1})\\
    \vdots
  \end{split}
\end{eqnarray*}
We assume time invariance
in that we expect the dynamics of the process
to be equivalent over sufficiently long time windows of equal length (i.e., stationarity).
Since an action executed in the present moment might have repercussions in the
far future, it turns out that the quantity to optimize is not the instantaneous
rewards $r(s, a)$, but a \textit{cumulative reward} estimate which takes into
account expected reward from action choices in the future. A common approach to
modeling this gathered outcome is the time-discounted cumulative reward% function
\begin{equation}
  \label{eq:cumr}
  G^\pi = \sum_{t=0}^{\infty}\gamma^{t}R_t =
  R_0 + \gamma R_1 + \gamma^2 R_2 + \ldots + \gamma^tR_t + \ldots
\end{equation}
This random variable
  \footnote{The reward outcome is random as it depends both on the environment's dynamics and the
  policy $\pi$ being executed. The exponential delay discounting function used
  here refers to the usual formulation in the field of reinforcement learning,
  although psychological experiments may also reveal other discounting regimes
  \citep{green2004discounting}.}
measures the cumulative reward of
following an action policy $\pi$.
%
Note that value buffering may be realized in the vmPFC by virtue of
this region's connections to the NAc of the reward system
~\citep{carlezon2009,haber1995,croxson2005quantitative}.
